The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-21 ms.Rmd
Add info on rerunworkflow, changeworkflow and crossvalidation.

@@

`zoon` workflows are re-runnable records of the data, code and results of an entire SDM analysis and can be easily reproduced, scrutinized and extended by the whole research community.

@@

Extra stuff workflows do (handle cross validation, run parallel methods/data comparisons).

>>>>

#### Crossvalidation

`workflow` sensibly handles cross-validation.
Process modules are used to split the data into a training and test set or into multiple folds so that each fold in turn will be held back and used as the test for the predictive ability of any fitted models.
The same test/train splits will be used for each analysis if the multiple models or methods are being used so that model performance measures are comparable.
Furthermore, the test/train splits are saved along with the workflow so that other researchers adding to a workflow can make fair comparisons. 
After models are fitted to these subsets of the data, they are also fitted to the entire dataset as this will provide the best models for predictions from further new data.

@@

@@

`zoon` workflows are re-runnable records of the data, code and results of an entire SDM analysis and can be easily reproduced, scrutinized and extended by the whole research community.
A zoon workflow returns an object of class `zoonWorkflow`.
This object contains all the information needed to reproduce the analysis.
This includes the original call, a record of the packages and modules used and their versions when the analysis was run as well as all the data and fitted models.

A workflow is reproducible, reusable and alterable by way of the functions `RerunWorkflow` and `ChangeWorkflow`.
Using `RerunWorkflow` a workflow object can be run from scratch or from part way though the analysis to avoid computationally slow steps.
`ChangeWorkflow` takes as it's arguments a workflow object and new selections for any or all of the workflow steps.
The workflow is then rerun from the first altered step.
